---
title: "Testing Tourist Module"
author: "Bruno Caetano Vidigal"
date: "22 October 2015"
output: pdf_document
---

In this document there are some statistics and summaries about the **Tourist Module**.

We need to compare the estimates for tourism consumption of **Tourist Module** for all the countries and commodities with **Food Data**.
The **estimates** for **tourism consumption** with **103 distincts countries** and **419 distincts commodities** are below:

```{r include=FALSE, cache=FALSE}
## Load required functions
library(faosws)
library(dplyr)
library(reshape2)
library(data.table)
library(faoswsUtil)
library(ggplot2)
```


```{r, echo=FALSE}
foodCode = "5141"

# 1. Pull in tourist data

DEBUG_MODE = Sys.getenv("R_DEBUG_MODE")
R_SWS_SHARE_PATH = Sys.getenv("R_SWS_SHARE_PATH")

if(!exists("DEBUG_MODE") || DEBUG_MODE == ""){
  token = "41558a20-c419-4821-8288-2dc7ccbc5ecf"
  GetTestEnvironment("https://hqlqasws1.hq.un.fao.org:8181/sws",token)

}

## set the keys to get the tourist data from the FAO working system

destinationAreaCodes <- faosws::GetCodeList("tourism", "tourist_flow",
                                            "destinationCountryM49")

originAreaCodes <- faosws::GetCodeList("tourism", "tourist_flow",
                                       "originCountryM49")

tourismElementCodes <- faosws::GetCodeList("tourism", "tourist_consumption",
                                           "tourismElement")

## set the year range to pull data from the SWS

swsContext.computationParams$startYear <- as.numeric(swsContext.computationParams$startYear)
swsContext.computationParams$endYear <- as.numeric(swsContext.computationParams$endYear)
if(swsContext.computationParams$startYear > swsContext.computationParams$endYear)
    stop("First Year should be smallest than End Year")
## yearRange <- swsContext.datasets[[1]]@dimensions$timePointYears@keys
yearRange <- swsContext.computationParams$startYear:swsContext.computationParams$endYear
yearRange <- as.character(yearRange)


##Pull the bidirectional movement data from SWS pertaining to tourist visitors
##to all countries

destinationCountryDim1 <- Dimension(name = "destinationCountryM49",
                                    keys = destinationAreaCodes[, code])


originCountryDim2 <- Dimension(name = "originCountryM49",
                               keys = originAreaCodes[, code])

tourismElementDim3 <- Dimension(name = "tourismElement", keys = ("60"))

timePointYearsDim4 <- Dimension(name = "timePointYears", keys = yearRange)

touristKey <- DatasetKey(domain = "tourism", dataset = "tourist_flow",
                  dimensions = list(destinationCountryDim1, originCountryDim2, 
                                    tourismElementDim3, timePointYearsDim4))

## download the first tourist data from the SWS

touristData.1 <- GetData(touristKey, flags = FALSE)

#cat("Tourist data loaded with ", nrow(touristData.1), " rows.")

## remove the tourismElement column which is of no value to me here
touristData.1 <- touristData.1[, which(!grepl("tourism", colnames(touristData.1))), with=FALSE]

## change column names to small simple ones representing destination, origin,
## year and overnight visitor number
setnames(touristData.1, old = colnames(touristData.1), new = c("dest", "orig", "year", "onVisNum"))

# 2. Pull in consumption data

## set the keys to get the tourist data from the FAO working system
touristAreaCodes = faosws::GetCodeList("tourism", "tourist_consumption",
                                "geographicAreaM49")

## Pull number of mean number of days stayed, and number of single-day visitors
## from SWS pertaining to visitors to all countries
consumptionCountryDim1 = Dimension(name = "geographicAreaM49", keys = touristAreaCodes [, code])
consumptionElementDim2 = Dimension(name = "tourismElement", keys = c("20", "30"))
timePointYearsDim3 = Dimension(name = "timePointYears", keys = yearRange)
consumptionKey = DatasetKey(domain = "tourism", dataset = "tourist_consumption",
                 dimensions = list(consumptionCountryDim1, consumptionElementDim2, timePointYearsDim3))

## download the bi-direction tourism data from the SWS
consumptionData.2 <- GetData(consumptionKey, flags = FALSE)

## set the column names to small simple ones representing destination, database
## element, year and value
setnames(consumptionData.2, old = colnames(consumptionData.2), new = c("dest", "element", "year", "value"))

# 3. Calculate tourists leaving/coming to country A, B, ...

## cast the data table to get it in long format
consumptionData.2.1 <- as.data.table(dcast(consumptionData.2, dest + year ~ element))

## change the column names to something readable, "onVisDays" stands for the
## mean number of days that overnight visitors stayed in the destination country.
## "totDayVisNum" is the number of people who visited the country but for a
## single day, e.g. from a cruise ship
setnames(consumptionData.2.1, old = colnames(consumptionData.2.1), new = c("dest", "year", "onVisDays",
                                               "totDayVisNum"))

## replace missing day visitor numbers (NA) with zero, because it won't effect
## end calculations, but NA's cause equations to fail
consumptionData.2.1$totDayVisNum[is.na(consumptionData.2.1$totDayVisNum)] <- 0

## merge the two data sets, one containing overnight visitor numbers and number
## of days they visited, the other data set the number of tourists travelling to
## and from each country
touristOverNightData.3 <- merge(touristData.1, consumptionData.2.1, by=c("dest", "year"), all.x = TRUE)

## rearrange the column order to make it easier to view
touristOverNightData.3 <- setcolorder(touristOverNightData.3, neworder = c("year", "orig", "dest", "onVisNum",
                                         "onVisDays", "totDayVisNum"))

## a small number of countries are missing values for overnight visitor days,
## "onVisDays" and this affects the bi-directional calculations for them, but
## also all of the other countries as well, so this imputes the missing number
## of days, by taking the mean of all day numbers present, grouped by year.
touristOverNightData.3[, onVisDays := ifelse(is.na(onVisDays), mean(onVisDays, na.rm=TRUE),
                            onVisDays), by = year]

## calculate the total number tourist visitor days, the product of overnight
## visitor number and days per visit
touristOverNightData.3[, onVisTotDays := onVisNum * onVisDays]


## calculate a new total overnight visitor number per country of destination, to
## be used later to proportion the day visitor number, because we do not have
## data for country of origin, and allocate them to a country of origin,
## assuming they arrive in the same relative proportions as the overnight
## visitors
touristOverNightData.3[, totOnVisNum := sum(onVisNum), by=list(year,dest)]

## create a new total visitor days by summing the overnight visitor days, and
## the day visitor days
touristOverNightData.3[, totVisDays := onVisTotDays + totDayVisNum]


## calculate total visitor days per year who leaves your country
daysOut.4 <- touristOverNightData.3[, list(daysOut = sum(totVisDays, na.rm = T)),
                 by = c('orig', 'year')]

## calculate total visitor days per year who comes to the country
daysIn.5 <- touristOverNightData.3[, list(daysIn = sum(totVisDays, na.rm = T)),
                by = c('dest', 'year')]

## change column name from "orig" to "country"
setnames(daysOut.4, 'orig', 'country')

## change column name from "dest" to "country"
setnames(daysIn.5, 'dest', 'country')

##-------------
## tourist data
##-------------

## merge daysOut and daysIn to allow calculation of days net per country and year
tourismDays.6 <- merge(daysOut.4, daysIn.5, by=c("country", "year"), all.x = TRUE)
tourismDays.6[, daysNet := daysIn - daysOut]

# Pull food consumption

## set the keys to get the calorie consumption, by individual FBS commodity for
## each country from the FAO working system
foodAreaCodes <- faosws::GetCodeList("agriculture", "agriculture", "geographicAreaM49")
foodElementCodes <- faosws::GetCodeList("suafbs", "fbs", "measuredElementSuaFbs")

## the Item codes contain a hierarchy.  We need to determine all the child
## nodes of the hierarchy and add them to get total consumption.
oldAreaCodes <- GetCodeList("agriculture", "agriculture", "geographicAreaM49")
itemCodes <- GetCodeList("agriculture", "agriculture", "measuredItemCPC")[, code]

## Pull the supply utilization account(SUA) food balance sheet (FBS) data from
## SWS pertaining to calorie consumption from each commodity in each country
countryCodeDim1 <- Dimension(name = "geographicAreaM49",
                  keys = oldAreaCodes[type == "country", code])
## A bit hackish: get population from total calories and total calories/person/day
foodCodeDim2 <- Dimension(name = "measuredElement", keys = c(foodCode))
itemCPCDim3 <- Dimension(name = "measuredItemCPC", keys = itemCodes)
timePointYearsDim4 <- Dimension(name = "timePointYears", keys = yearRange)
calorieConsumptionKey <- DatasetKey(domain = "agriculture", dataset = "agriculture",
                  dimensions = list(countryCodeDim1, foodCodeDim2, itemCPCDim3, timePointYearsDim4))

## download the calorie consumption data from the SWS
calorieConsumptionData.7 <- GetData(calorieConsumptionKey, flags = FALSE)

calorieConsumptionData.7.1 <- dcast.data.table(calorieConsumptionData.7,
                          geographicAreaM49 + measuredItemCPC + timePointYears ~ measuredElement,
                          value.var = "Value")

## set the column names to small simple ones representing destination cuntry, database
## element, year and total calories
setnames(calorieConsumptionData.7.1, old = c("geographicAreaM49", "measuredItemCPC", "timePointYears", "5141"),
         new = c("country", "item", "year", "totalCal"))


## Pull the population datasets

countryCodePopDim1 <- Dimension(name = "geographicAreaM49",
                  keys = oldAreaCodes[type == "country", code])
elementPopDim2 <- Dimension(name = "measuredElementPopulation", keys = c("21"))
timePointYearsDim3 <- Dimension(name = "timePointYears", keys = yearRange)
popKey <- DatasetKey(domain = "population", dataset = "population",
                  dimensions = list(countryCodePopDim1, elementPopDim2, timePointYearsDim3))

## download the population data from the SWS
popData.8 <- GetData(popKey, flags = FALSE)

popData.8.1 <- dcast.data.table(popData.8,
                          geographicAreaM49 + timePointYears ~ measuredElementPopulation,
                          value.var = "Value")

## set the column names to small simple ones representing destination cuntry, 
##  year and total population
setnames(popData.8.1, old = c("geographicAreaM49", "timePointYears", "21"),
         new = c("country", "year", "pop"))


## Merge population data with food data

setkey(calorieConsumptionData.7.1, "country", "year")
setkey(popData.8.1, "country", "year")

calorieConsumptionPopData.9 <- merge(calorieConsumptionData.7.1, popData.8.1, by = c("country", "year"), 
               all.x = TRUE )

## compute total calories per person per day in orig country
## Population is in 1000s
calorieConsumptionPopData.9[, calPerPersonPerDay := totalCal / 365 / (pop * 1000)]

## merge data8 and data5 to allow calculation of calories 
## by commodity per year for who goes to the country and who left  

setkey(tourismDays.6, "country", "year")
setkey(calorieConsumptionPopData.9, "country", "year")

caloriesCommoditiesTourist.10 <- merge(calorieConsumptionPopData.9, tourismDays.6, by = c("country", "year"), 
      all.x = T)

caloriesCommoditiesTourist.10[, calOutCountry := daysOut * calPerPersonPerDay]
caloriesCommoditiesTourist.10[, calInCountry := daysIn * calPerPersonPerDay]
caloriesCommoditiesTourist.10[, calNetCountry := daysNet * calPerPersonPerDay]

## Get rid of some of the columns that we don't need anymore:

caloriesCommoditiesTourist.10[, c("totalCal", "pop", "calPerPersonPerDay", "daysOut", 
          "daysIn", "daysNet") := NULL]

## Net calories
touristCaloriesNetCountryByItem.11 <- caloriesCommoditiesTourist.10[ , list(calNetCountry),
                                          by = list(year, country, item) ]

touristCaloriesNetCountryByItem.11[, tourismElement:= "100"]
touristCaloriesNetCountryByItem.11[, flagObservationStatus:= "I"]
touristCaloriesNetCountryByItem.11[, flagMethod:= "e"]
```

```{r, echo=FALSE}
head(touristCaloriesNetCountryByItem.11)
```

The **Food Data** with **103 distincts countries** and **419 distincts commodities** are below:

```{r, echo=FALSE}
head(calorieConsumptionData.7.1)
```

**Merging** these datasets:

```{r, echo=FALSE}
## Merge Tourism data with food data
testingTouristData <- merge(touristCaloriesNetCountryByItem.11, calorieConsumptionData.7.1, 
      by = c("year", "country", "item"))

head(testingTouristData)
```

Now we can calculate **% tourism consumption** per country and per commoditie. 
```{r, echo=FALSE}
## % tourism consumption per country and item
testingTouristData[, percentCalItemCountry := calNetCountry/totalCal]
head(testingTouristData)
```

<<<<<<< HEAD
#save(testingTouristData, file = "~/Github/faoswsTourist/Data/testingTouristData.RData")

## % consumption per country
=======
When the estimates for tourism consumption is **negative** it means that more people **left this country**. If is **positive**, it means more people **went** to this country.
So we can calculate which countries were more impacted with tourism consumption and which one had less tourism consumption in 2012.
>>>>>>> 61cac3eb259913904d96f0663cf3da4dfb726076

````{r, echo = FALSE}
tabCountry1 <- testingTouristData[, list(percentCalCountry = sum(calNetCountry, na.rm=T)/sum(totalCal, na.rm=T)),
                   by = list(year, country)]
````

<<<<<<< HEAD
#save(tabCountry, file = "~/Github/faoswsTourist/Data/tabCountry.RData")

mapData <- data.table(map_data(map = "world"))
setnames(mapData, old = c("long", "lat", "group", "order", "region", "subregion"),
                          new = c("long", "lat", "group", "order", "country", "subregion"))
=======
Summary of estimates tourism consumption:
```{r, echo=FALSE}
if(Sys.info()[7] == "rockc_000"){
    load("~/GitHub/faoswsTourist/Data/tabCountry.RData")
    tabCountry1 <- tabCountry
    setnames(tabCountry1, "percentCaloriesCountry", "percentCalCountry")
}
summary(tabCountry1$percentCalCountry)
```
>>>>>>> 61cac3eb259913904d96f0663cf3da4dfb726076

**Top 5 positive** estimated consumption per country for tourism. **Bahamas (44)** and **Seychelles (690)** are the two firsts countries with more % tourism consumption.
````{r, echo = FALSE}

tabCountry1 <- tabCountry1[order(-tabCountry1$percentCalCountry)]
tabCountry1[, rank := 1:nrow(tabCountry1)]
head(tabCountry1, 5)
````

**Top 5 negative** estimated consumption per country for tourism. Note that **Albania (8)** has a strange number. It's necessary to check it.
````{r, echo = FALSE}
tail(tabCountry1, 5)
````

The decis are:
```{r, echo=FALSE}
quantile(tabCountry1$percentCalCountry, na.rm = T, 
         probs = c(0:9)/10)
```
The histogram and BoxPlot are below:

```{r, echo=FALSE}
par(mfrow=c(1, 2))
hist(tabCountry1$percentCalCountry, breaks = 100, xlab="% Tourism consumption", main = "")
boxplot(tabCountry1$percentCalCountry)
```

If we remove **Albania** this analyze, the new plots are:

```{r, echo=FALSE}
tabCountry1.1 <- tabCountry1[country != 8]
par(mfrow=c(1, 2))
hist(tabCountry1.1$percentCalCountry, xlab="% Tourism consumption", main = "")
boxplot(tabCountry1.1$percentCalCountry)
```

With this data, we have this % below about tourism consumption.
```{r, echo=FALSE}
tabCountry1[, consumption := ifelse(percentCalCountry > 0, "positive",
                                    ifelse(percentCalCountry < 0, "negative", "zero"))]
t1 <- tabCountry1[, .N, consumption]
t1[, percent := 100*round(N/sum(N), 3)]
t1
```

```{r, echo = FALSE}
## Load fao_world object
load(url("https://github.com/UNFAOstatistics/gisfao/raw/master/data/fao_world.RData"))
# Install development version of ggplot2
devtools::install_github("hadley/ggplot2")
coords <- ggplot2:::fortify(fao_world)
countryMap <- as.character(fao_world$ADM0_NAME)
countryMap <- data.frame(id = 0:(length(countryMap)-1),
                         country = countryMap)
coords <- merge(coords, countryMap, by = "id", all = TRUE)
coords <- merge(coords, tabCountry1, by = "country", all = TRUE)
coords <- coords[order(coords$country, coords$piece, coords$order), ]
coords[coords$percentCalCountry < -.5 & !is.na(coords$percentCalCountry), ]
ggplot(coords, aes(x = long, y = lat, group = group)) +
    geom_path() +
    geom_polygon(aes(fill = percentCalCountry, group = group))

coords <- ggplot2:::fortify(fao_world)
countryMap <- as.character(fao_world$FAOST_CODE)
countryMap <- data.frame(id = 0:(length(countryMap)-1),
                         countryCode = countryMap)
coords <- merge(coords, countryMap, by = "id", all = TRUE)
coords <- merge(coords, tabCountry1, by = "countryCode", all = TRUE)
coords <- coords[order(coords$country, coords$piece, coords$order), ]
coords[coords$percentCalCountry < -.5 & !is.na(coords$percentCalCountry), ]
ggplot(coords, aes(x = long, y = lat, group = group)) +
    geom_path() +
    geom_polygon(aes(fill = percentCalCountry, group = group))
```