---
title: "Testing Tourist Module"
author: "Bruno Caetano Vidigal"
date: "28 October 2015"
output: pdf_document
---

# About this document

In this document there are some statistics and summaries about the **Tourist Module** in 2012.

We need to compare the estimates for tourism consumption of **Tourist Module** for all the countries and the commodities with **Food Data**.


```{r include=FALSE, cache=FALSE}
## Load required functions
library(faosws)
library(dplyr)
library(reshape2)
library(data.table)
library(faoswsUtil)
library(ggplot2)
library(countrycode)
library(scales)
```

```{r include=FALSE, cache=FALSE}

foodCode = "5141"

# 1. Pull in tourist data

DEBUG_MODE = Sys.getenv("R_DEBUG_MODE")
R_SWS_SHARE_PATH = Sys.getenv("R_SWS_SHARE_PATH")

if(!exists("DEBUG_MODE") || DEBUG_MODE == ""){
  token = "41558a20-c419-4821-8288-2dc7ccbc5ecf"
  GetTestEnvironment("https://hqlqasws1.hq.un.fao.org:8181/sws",token)
  
}

## set the keys to get the tourist data from the FAO working system

destinationAreaCodes <- faosws::GetCodeList("tourism", "tourist_flow",
                                            "destinationCountryM49")

originAreaCodes <- faosws::GetCodeList("tourism", "tourist_flow",
                                       "originCountryM49")

tourismElementCodes <- faosws::GetCodeList("tourism", "tourist_consumption",
                                           "tourismElement")

## set the year range to pull data from the SWS

swsContext.computationParams$startYear <- as.numeric(swsContext.computationParams$startYear)
swsContext.computationParams$endYear <- as.numeric(swsContext.computationParams$endYear)
if(swsContext.computationParams$startYear > swsContext.computationParams$endYear)
  stop("First Year should be smallest than End Year")
## yearRange <- swsContext.datasets[[1]]@dimensions$timePointYears@keys
yearRange <- swsContext.computationParams$startYear:swsContext.computationParams$endYear
yearRange <- as.character(yearRange)


##Pull the bidirectional movement data from SWS pertaining to tourist visitors
##to all countries

destinationCountryDim1 <- Dimension(name = "destinationCountryM49",
                                    keys = destinationAreaCodes[, code])


originCountryDim2 <- Dimension(name = "originCountryM49",
                               keys = originAreaCodes[, code])

tourismElementDim3 <- Dimension(name = "tourismElement", keys = ("60"))

timePointYearsDim4 <- Dimension(name = "timePointYears", keys = yearRange)

touristKey <- DatasetKey(domain = "tourism", dataset = "tourist_flow",
                         dimensions = list(destinationCountryDim1, originCountryDim2, 
                                           tourismElementDim3, timePointYearsDim4))

## download the first tourist data from the SWS

touristData.1 <- GetData(touristKey, flags = FALSE)

#cat("Tourist data loaded with ", nrow(touristData.1), " rows.")

## remove the tourismElement column which is of no value to me here
touristData.1 <- touristData.1[, which(!grepl("tourism", colnames(touristData.1))), with=FALSE]

## change column names to small simple ones representing destination, origin,
## year and overnight visitor number
setnames(touristData.1, old = colnames(touristData.1), new = c("dest", "orig", "year", "onVisNum"))

# 2. Pull in consumption data

## set the keys to get the tourist data from the FAO working system
touristAreaCodes = faosws::GetCodeList("tourism", "tourist_consumption",
                                       "geographicAreaM49")

## Pull number of mean number of days stayed, and number of single-day visitors
## from SWS pertaining to visitors to all countries
consumptionCountryDim1 = Dimension(name = "geographicAreaM49", keys = touristAreaCodes [, code])
consumptionElementDim2 = Dimension(name = "tourismElement", keys = c("20", "30"))
timePointYearsDim3 = Dimension(name = "timePointYears", keys = yearRange)
consumptionKey = DatasetKey(domain = "tourism", dataset = "tourist_consumption",
                            dimensions = list(consumptionCountryDim1, consumptionElementDim2, timePointYearsDim3))

## download the bi-direction tourism data from the SWS
consumptionData.2 <- GetData(consumptionKey, flags = FALSE)

## set the column names to small simple ones representing destination, database
## element, year and value
setnames(consumptionData.2, old = colnames(consumptionData.2), new = c("dest", "element", "year", "value"))

# 3. Calculate tourists leaving/coming to country A, B, ...

## cast the data table to get it in long format
consumptionData.2.1 <- as.data.table(dcast(consumptionData.2, dest + year ~ element))

## change the column names to something readable, "onVisDays" stands for the
## mean number of days that overnight visitors stayed in the destination country.
## "totDayVisNum" is the number of people who visited the country but for a
## single day, e.g. from a cruise ship
setnames(consumptionData.2.1, old = colnames(consumptionData.2.1), new = c("dest", "year", "onVisDays",
                                                                           "totDayVisNum"))

## replace missing day visitor numbers (NA) with zero, because it won't effect
## end calculations, but NA's cause equations to fail
consumptionData.2.1$totDayVisNum[is.na(consumptionData.2.1$totDayVisNum)] <- 0

## merge the two data sets, one containing overnight visitor numbers and number
## of days they visited, the other data set the number of tourists travelling to
## and from each country
touristOverNightData.3 <- merge(touristData.1, consumptionData.2.1, by=c("dest", "year"), all.x = TRUE)

## rearrange the column order to make it easier to view
touristOverNightData.3 <- setcolorder(touristOverNightData.3, neworder = c("year", "orig", "dest", "onVisNum",
                                                                           "onVisDays", "totDayVisNum"))

## a small number of countries are missing values for overnight visitor days,
## "onVisDays" and this affects the bi-directional calculations for them, but
## also all of the other countries as well, so this imputes the missing number
## of days, by taking the mean of all day numbers present, grouped by year.
touristOverNightData.3[, onVisDays := ifelse(is.na(onVisDays), mean(onVisDays, na.rm=TRUE),
                                             onVisDays), by = year]

## calculate the total number tourist visitor days, the product of overnight
## visitor number and days per visit
touristOverNightData.3[, onVisTotDays := onVisNum * onVisDays]


## calculate a new total overnight visitor number per country of destination, to
## be used later to proportion the day visitor number, because we do not have
## data for country of origin, and allocate them to a country of origin,
## assuming they arrive in the same relative proportions as the overnight
## visitors
touristOverNightData.3[, totOnVisNum := sum(onVisNum), by=list(year,dest)]

## create a new total visitor days by summing the overnight visitor days, and
## the day visitor days
touristOverNightData.3[, totVisDays := onVisTotDays + totDayVisNum]


## calculate total visitor days per year who leaves your country
daysOut.4 <- touristOverNightData.3[, list(daysOut = sum(totVisDays, na.rm = T)),
                                    by = c('orig', 'year')]

## calculate total visitor days per year who comes to the country
daysIn.5 <- touristOverNightData.3[, list(daysIn = sum(totVisDays, na.rm = T)),
                                   by = c('dest', 'year')]

## change column name from "orig" to "country"
setnames(daysOut.4, 'orig', 'country')

## change column name from "dest" to "country"
setnames(daysIn.5, 'dest', 'country')

##-------------
## tourist data
##-------------

## merge daysOut and daysIn to allow calculation of days net per country and year
tourismDays.6 <- merge(daysOut.4, daysIn.5, by=c("country", "year"), all.x = TRUE)
tourismDays.6[, daysNet := daysIn - daysOut]

# Pull food consumption

## set the keys to get the calorie consumption, by individual FBS commodity for
## each country from the FAO working system
foodAreaCodes <- faosws::GetCodeList("agriculture", "agriculture", "geographicAreaM49")
foodElementCodes <- faosws::GetCodeList("suafbs", "fbs", "measuredElementSuaFbs")

## the Item codes contain a hierarchy.  We need to determine all the child
## nodes of the hierarchy and add them to get total consumption.
oldAreaCodes <- GetCodeList("agriculture", "agriculture", "geographicAreaM49")
itemCodes <- GetCodeList("agriculture", "agriculture", "measuredItemCPC")[, code]

## Pull the supply utilization account(SUA) food balance sheet (FBS) data from
## SWS pertaining to calorie consumption from each commodity in each country
countryCodeDim1 <- Dimension(name = "geographicAreaM49",
                             keys = oldAreaCodes[type == "country", code])
## A bit hackish: get population from total calories and total calories/person/day
foodCodeDim2 <- Dimension(name = "measuredElement", keys = c(foodCode))
itemCPCDim3 <- Dimension(name = "measuredItemCPC", keys = itemCodes)
timePointYearsDim4 <- Dimension(name = "timePointYears", keys = yearRange)
calorieConsumptionKey <- DatasetKey(domain = "agriculture", dataset = "agriculture",
                                    dimensions = list(countryCodeDim1, foodCodeDim2, itemCPCDim3, timePointYearsDim4))

## download the calorie consumption data from the SWS
calorieConsumptionData.7 <- GetData(calorieConsumptionKey, flags = FALSE)

calorieConsumptionData.7.1 <- dcast.data.table(calorieConsumptionData.7,
                                               geographicAreaM49 + measuredItemCPC + timePointYears ~ measuredElement,
                                               value.var = "Value")

## set the column names to small simple ones representing destination cuntry, database
## element, year and total calories
setnames(calorieConsumptionData.7.1, old = c("geographicAreaM49", "measuredItemCPC", "timePointYears", "5141"),
         new = c("country", "item", "year", "totalCal"))


## Pull the population datasets

countryCodePopDim1 <- Dimension(name = "geographicAreaM49",
                                keys = oldAreaCodes[type == "country", code])
elementPopDim2 <- Dimension(name = "measuredElementPopulation", keys = c("21"))
timePointYearsDim3 <- Dimension(name = "timePointYears", keys = yearRange)
popKey <- DatasetKey(domain = "population", dataset = "population",
                     dimensions = list(countryCodePopDim1, elementPopDim2, timePointYearsDim3))

## download the population data from the SWS
popData.8 <- GetData(popKey, flags = FALSE)

popData.8.1 <- dcast.data.table(popData.8,
                                geographicAreaM49 + timePointYears ~ measuredElementPopulation,
                                value.var = "Value")

## set the column names to small simple ones representing destination cuntry, 
##  year and total population
setnames(popData.8.1, old = c("geographicAreaM49", "timePointYears", "21"),
         new = c("country", "year", "pop"))


## Merge population data with food data

setkey(calorieConsumptionData.7.1, "country", "year")
setkey(popData.8.1, "country", "year")

calorieConsumptionPopData.9 <- merge(calorieConsumptionData.7.1, popData.8.1, by = c("country", "year"), 
                                     all.x = TRUE )

## compute total calories per person per day in orig country
## Population is in 1000s
calorieConsumptionPopData.9[, calPerPersonPerDay := totalCal / 365 / (pop * 1000)]

## merge data8 and data5 to allow calculation of calories 
## by commodity per year for who goes to the country and who left  

setkey(tourismDays.6, "country", "year")
setkey(calorieConsumptionPopData.9, "country", "year")

caloriesCommoditiesTourist.10 <- merge(calorieConsumptionPopData.9, tourismDays.6, by = c("country", "year"), 
                                       all.x = T)

caloriesCommoditiesTourist.10[, calOutCountry := daysOut * calPerPersonPerDay]
caloriesCommoditiesTourist.10[, calInCountry := daysIn * calPerPersonPerDay]
caloriesCommoditiesTourist.10[, calNetCountry := daysNet * calPerPersonPerDay]

## Calories in, out, net and total per country
consumpCal <- caloriesCommoditiesTourist.10[, list(totalCal = sum(totalCal),
                                     totalCalOutCountry = sum(calOutCountry),
                                     totalCalInCountry = sum(calInCountry),
                                     totalCalNetCountry = sum(calNetCountry)),
                              by = list(country, year)]


## Get rid of some of the columns that we don't need anymore:

caloriesCommoditiesTourist.10[, c("totalCal", "pop", "calPerPersonPerDay", "daysOut", 
                                  "daysIn", "daysNet") := NULL]

## Net calories
touristCaloriesNetCountryByItem.11 <- caloriesCommoditiesTourist.10[ , list(calNetCountry),
                                                                     by = list(year, country, item) ]

touristCaloriesNetCountryByItem.11[, tourismElement:= "100"]
touristCaloriesNetCountryByItem.11[, flagObservationStatus:= "I"]
touristCaloriesNetCountryByItem.11[, flagMethod:= "e"]

cpcCode <- GetCodeList("agriculture", "agriculutre", "measuredItemCPC")[, code, description]
setnames(cpcCode, old = c("description", "code"), new = c("Item", "item"))

m49Code <- GetCodeList("agriculture", "agriculutre", "geographicAreaM49")[, code, description]
setnames(m49Code, old = c("description", "code"), new = c("Country", "country"))

## Merge
touristNetCaloriesData <- merge(touristCaloriesNetCountryByItem.11, m49Code, by = c("country"), all.x = T)
touristNetCaloriesData <- merge(touristNetCaloriesData, cpcCode, by = c("item"), all.x = T)

touristNetCaloriesData[, c("tourismElement", "flagObservationStatus", "flagMethod") := NULL ]

setnames(touristNetCaloriesData,
         old = c("item", "country", "year", "calNetCountry", "Country", "Item"),
         new = c("itemCode", "countryCode", "year", "netCalories", "country", "item"))


foodData <- merge(calorieConsumptionData.7.1, m49Code, by = c("country"), all.x = T)
foodData <- merge(foodData, cpcCode, by = c("item"), all.x = T)
foodData[, c("item", "country") := NULL ]

setnames(foodData,
         old = c("year", "totalCal", "Country", "Item"),
         new = c("year", "totalCalories", "country", "item"))

setcolorder(foodData,
            c("year", "country", "item", "totalCalories"))

## Merge Tourism data with food data
testingTouristData <- merge(touristNetCaloriesData, foodData, 
                            by = c("year", "country", "item"))

## % tourism consumption per country and item
testingTouristData[, percentCalories := netCalories/totalCalories]

## % consumption per country

tabCountry <- testingTouristData[, list(percentCaloriesCountry = sum(netCalories, na.rm=T)/sum(totalCalories, na.rm=T)),
                                 by = list(year, country, countryCode)]

````

```{r include=FALSE, cache=FALSE}
## world map is working now
## Load fao_world object
load(url("https://github.com/UNFAOstatistics/gisfao/raw/master/data/fao_world.RData"))
# Install development version of ggplot2
#devtools::install_github("hadley/ggplot2")
coords <- ggplot2:::fortify(fao_world)
countryMap <- as.character(fao_world$ADM0_NAME)
countryMap <- data.frame(id = 0:(length(countryMap)-1),
                         country = countryMap)
coords <- merge(coords, countryMap, by = "id", all = TRUE)

## use countryCode package

tabCountry <- data.frame(tabCountry)
tabCountry$shortName <- countrycode(tabCountry$country, "country.name", "iso3c")

coords$shortName <- countrycode(coords$country, "country.name", "iso3c")
# unique(subset(coords, is.na(shortName) == T)$country)

coords <- merge(coords, tabCountry, by = "shortName", all = TRUE)
coords <- coords[order(coords$shortName, coords$piece, coords$order), ]
coords[coords$percentCaloriesCountry < -.5 & !is.na(coords$percentCaloriesCountry), ]

## Create a categorical variable

coords <- data.table(coords)
coords[, percentCat := ifelse(is.na(percentCaloriesCountry) == T, "Missing", 
                               ifelse(percentCaloriesCountry > 0, "Receiver",
                                     ifelse(percentCaloriesCountry < 0, "Emitter", "Neutro")))]

coords$percentCat <- factor(coords$percentCat, 
                             levels = c("Missing", "Emitter", "Neutro", "Receiver"))

## Validation
tabValidation <- coords[, list(country.y = unique(country.y)),
       by=list(country.x)]
#tabValidation[is.na(country.x) == T]
setnames(tabValidation, c("country.x", "country.y"), c("countryFaoWorld", "countryTouristConsumption"))
#tabValidation[is.na(countryFaoWorld) == T]

## 10 countries that we need to put in fao_world table
## save(tabValidation, file = "~/Github/faoswsTourist/Data/tabValidation.RData")

####################################################
### validation with map.dat <- map_data("world") ###
####################################################
#mapData <- map_data("world")
#head(subset(mapData, region == "Seychelles"))
#tabCountry$shortName <- countrycode(tabCountry$country, "country.name", "iso3c")
#mapData$shortName <- countrycode(mapData$region, "country.name", "iso3c")

## merge these datasets
#mapDataCal <- merge(mapData, tabCountry, by = "shortName", all = T)

#mapDataCal <- data.table(mapDataCal)
#mapDataCal[, percentCat := ifelse(is.na(percentCaloriesCountry) == T, "Missing", 
 #                             ifelse(percentCaloriesCountry > 0, "Receiver",
  #                                   ifelse(percentCaloriesCountry < 0, "Emitter", "Neutro")))]

#mapDataCal$percentCat <- factor(mapDataCal$percentCat, 
 #                           levels = c("Missing", "Emitter", "Neutro", "Receiver"))

#mapDataCal <- mapDataCal[order(mapDataCal$shortName, mapDataCal$order), ]

#ggplot(mapDataCal, aes(x=long, y=lat, group=group, fill=percentCat)) + 
 # geom_polygon() + #theme(legend.title=element_blank()) +
  #scale_fill_manual(values=c("#C0C0C0", "#D00000", "#fec666", "#667bc6")) +
  #theme(#line = element_blank(),
   # axis.ticks = element_blank(),
    #axis.text.x = element_blank(), 
    #axis.text.y = element_blank(),
    ##text = element_blank(),
    #title = element_blank())
#####################################################

````

````{r include=FALSE, cache=FALSE}

# First map! It's working but I prefer to put the second one.
#options(warn=-1)
#ggplot(coords, aes(x=long, y=lat, group=group, fill=percentCat)) + 
 # geom_polygon() + #theme(legend.title=element_blank()) +
  #scale_fill_manual(values=c("#C0C0C0", "#D00000", "#fec666", "#667bc6")) +
  #theme(#line = element_blank(),
   #     axis.ticks = element_blank(),
    #    axis.text.x = element_blank(), 
     #   axis.text.y = element_blank(),
        #text = element_blank(),
      #  title = element_blank())
````

````{r include=FALSE, cache=FALSE}
options(warn=-1)
## Let's to compare calories consumption by tourist inside and outside the 
## country with the mean consumption of the world.  

#consumpCal[is.na(totalCal) == T]
#consumpCal[is.na(totalCalOutCountry) == T]
#consumpCal[is.na(totalCalInCountry) == T]

consumpCal[, percentcalOut := totalCalOutCountry/totalCal]
consumpCal[, percentcalIn := totalCalInCountry/totalCal]

## Merge
consumpCal <- merge(consumpCal, m49Code, by="country", all.x = T)

## Let's divide in 2 parts and then to make rbind to join again

# Just countries with value for consumption
consumpCal.1 <- consumpCal[is.na(totalCalOutCountry) != T & is.na(totalCalInCountry) != T]

consumpCal.1[, clusterCountry := ifelse(percentcalOut < sum(totalCalOutCountry, na.rm=T)/sum(totalCal, na.rm=T) & 
                                        percentcalIn < sum(totalCalInCountry, na.rm=T)/sum(totalCal, na.rm=T), "Isolated",
                                      ifelse(percentcalOut < sum(totalCalOutCountry, na.rm=T)/sum(totalCal, na.rm=T) & 
                                               percentcalIn > sum(totalCalInCountry, na.rm=T)/sum(totalCal, na.rm=T), "Receiver",
                                             ifelse(percentcalOut > sum(totalCalOutCountry, na.rm=T)/sum(totalCal, na.rm=T) & 
                                                      percentcalIn < sum(totalCalInCountry, na.rm=T)/sum(totalCal, na.rm=T), "Emitter", 
                                                    ifelse(percentcalOut > sum(totalCalOutCountry, na.rm=T)/sum(totalCal, na.rm=T) & 
                                                             percentcalIn > sum(totalCalInCountry, na.rm=T)/sum(totalCal, na.rm=T), "Transit", 
                                                           "Missing"))))]

# Just countries with NA for consumption IN or OUT
consumpCal.2 <- consumpCal[is.na(totalCalOutCountry) == T | is.na(totalCalInCountry) == T]
consumpCal.2[, clusterCountry := "Missing"]

## Rbind this datasets

consumpCal <- rbind(consumpCal.1, consumpCal.2)
#head(consumpCal)
#table(consumpCal$clusterCountry)

## Load fao_world object
load(url("https://github.com/UNFAOstatistics/gisfao/raw/master/data/fao_world.RData"))
# Install development version of ggplot2
#devtools::install_github("hadley/ggplot2")
coords <- ggplot2:::fortify(fao_world)
countryMap <- as.character(fao_world$ADM0_NAME)
countryMap <- data.frame(id = 0:(length(countryMap)-1),
                         country = countryMap)
coords <- merge(coords, countryMap, by = "id", all = TRUE)

## use countryCode package
consumpCal <- data.frame(consumpCal)
consumpCal$shortName <- countrycode(consumpCal$Country, "country.name", "iso3c")
coords$shortName <- countrycode(coords$country, "country.name", "iso3c")

## Merge
coords2 <- merge(coords, consumpCal, by = "shortName", all = TRUE)
coords2 <- coords2[order(coords2$shortName, coords2$piece, coords2$order), ]
coords2 <- data.table(coords2)
coords2[is.na(clusterCountry) == T, clusterCountry := "Missing"]
coords2$clusterCountry <- factor(coords2$clusterCountry, 
                             levels = c("Missing", "Emitter", "Isolated", "Receiver", "Transit"))

countriesNames <- coords2
````

## Segmentation of the world according to a tourist consumption


For our first visualization, we divided the countries in five clusters.


**Receiver**: countries with % outside of consumption tourists under the average and % consumption inside over the average.

**Emitter**: countries with % inside of consumption tourists under the average and % consumption outside over the average.

**Transit**: countries with both % of consumption inside and outside over the average consumption of tourists. 

**Isolated**: countries with both % of consumption inside and outside under the average consumption of tourists. 

**Missing**: countries with no data for tourist consumption.

There are information for 74 countries (39.5%) and the others countries are missing data.

According to a cluster, we have:

**Cluster** | **Countries %**
------------- | -------------
Receiver      |    3.7%
Emitter       |    4.3% 
Transit       |    12.3%
Isolated      |    19.2% 
Missing       |    60.5%


````{r, echo=FALSE}
options(warn=-1)
ggplot(coords2, aes(x=long, y=lat, group=group, fill=clusterCountry)) + 
  geom_polygon() + #theme(legend.title=element_blank()) +
  scale_fill_manual(values=c("#C0C0C0", "#D00000", "#fec666", "#667bc6", "#2E8B57")) +
  #geom_point() + 
  #geom_text(label=country.x) +
  theme(#line = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        #text = element_blank(),
        title = element_blank())
````


## Summaries


Above there are some statistics about the **Net Tourist Consumption** estimated by **Tourist Module**.

Note that when the estimates for tourist consumption is **negative** it means that more people **left this country**. If is **positive**, it means that more people **went** to this country.

Statistics | Values
------------- | -------------
 Min       | - 67%
 Mean      | - 0.5% 
 Max       |  6.3%


This result it means that the country more impacted with the tourist consumption had 6.3% of your production
consumed by tourists. About the minimum value, we need to investigate what is happening.

So we can calculate which countries were more impacted with the tourist consumption and which one had less tourist consumption in 2012.
````{r include=FALSE, cache=FALSE}
consumpCal <- data.table(consumpCal)
consumpCal[, percentNet := totalCalNetCountry/totalCal]
#100*summary(consumpCal$percentNet)
````

The histogram above is about the net food consumption % of tourists. Note that there is just one country (**Albania**) with the strange negative value.


````{r, echo=FALSE}
hist(100*consumpCal$percentNet, breaks = 100, xlab = "Net Food Consumption % of Tourists", main="")
````

Let's check the **overnight visitor numbers** from 5 regions that had higher growth from 2010 to 2012.
So, we can see that is no make sense the values for **Albania**.

````{r, echo=FALSE}
touristFlow <- touristData.1[, list(totOnVisNum = sum(onVisNum)),
              by = list(orig, year)]

touristFlow.1 <- as.data.table(dcast(touristFlow, orig ~ year, value.var = "totOnVisNum"))

setnames(touristFlow.1, old = c("orig", "2010", "2011", "2012"),
         new = c("country", "year2010", "year2011", "year2012"))

touristFlow.1[, percentIncreasing := 100*round((year2012 - year2010)/year2010, 3), ]

touristFlow.1 <- merge(touristFlow.1, m49Code, by = "country", all.x=T)
touristFlow.1 <- touristFlow.1[order(-touristFlow.1$percentIncreasing)]
top5TouristFlow <- head(touristFlow.1, 5)
top5TouristFlow$Country <- factor(top5TouristFlow$Country, 
                          levels = c("Albania", "Dng Ant EAA", "Congo", "Andorra", "Suriname"))

````

````{r, echo=FALSE, fig.width=6, fig.height=3}

space <- function(x, ...) { 
  format(x, ..., big.mark = ",", scientific = FALSE, trim = TRUE)
}

theme_fao <- function(angle=90, fonte="calibri", size=14) {
  
  theme(panel.grid.major = element_blank()) +
    theme(panel.background = element_blank())+
    theme(legend.title = element_text(family=fonte, size = size, face = "bold")) +
    theme(legend.text = element_text(family=fonte, size = size, face = "bold")) +
    theme(plot.title = element_text(family=fonte, size = size, face = "bold")) +
    theme(axis.text.x = element_text(family=fonte, size = size, face = "bold", angle = angle, vjust = .5))+ 
    theme(axis.text.y= element_text(family=fonte, size = size, face = "bold")) +
    theme(axis.title.x= element_text(family=fonte, size = size, face = "bold")) +
    theme(axis.title.y= element_text(family=fonte, size = size, face = "bold"))
  
}

p <- ggplot(data=top5TouristFlow, aes(x=as.factor(Country), y=percentIncreasing, 
                                      fill=as.factor(Country))) + 
  geom_bar(aes(), stat = "identity", position=position_dodge()) + 
  scale_y_continuous(labels = space) +
  theme(legend.position="none") +  ylab('growth %') + xlab('') + 
  #theme_fao(45) +
  annotate("text", x = 1, y = 10000, label = "46,000%") +
  annotate("text", x = 2, y = 10000, label = "1,680%") +
  annotate("text", x = 3, y = 10000, label = "226%") +
  annotate("text", x = 4, y = 10000, label = "208%") +
  annotate("text", x = 5, y = 10000, label = "192%")
p

````


## Countries more impacted by Tourist Consumption

````{r include=FALSE, cache=FALSE}
consumpCal <- consumpCal[order(-consumpCal$percentNet)]
````

Into some small islands states which are popular holiday destinations, such as the Bahamas or Seychelles, the Tourist Consumption can constituite a significant part in the uses of food products. 

Country     | % Net Tourist Consumption
--------------------- | -------------
 Bahamas    |         6.3%
 Seychelles |         5% 
 Barbados   |         4.6%
 Bermuda    |         4.3% 
 Cyprus     |         4%


## Countries less impacted by Tourist Consumption

````{r include=FALSE, cache=FALSE}
consumpCal <- consumpCal[order(-consumpCal$percentNet)]
````

These countries are the less impacted by tourist consumption. It means that more people left these countries than went to these countries.

Country     | % Net Tourist Consumption
----------- | -------------
 Albania                 |         - 67%
 Brunei Darussalam       |         - 5.8% 
 Republic of Moldova     |         - 2.7%
 Switzerland             |         - 2.6% 
 Kuwait                  |         - 2.2%

