---
title: "Tourist Module"
author: "Bruno Caetano Vidigal"
date: "1 February 2016"
output: pdf_document
---

# About this document

In this document there are some statistics and summaries about the **Tourist Module** in 2012.

We need to compare the estimates for tourism consumption of **Tourist Module** for all the countries and the commodities with **Food Data**.


```{r include=FALSE, cache=FALSE}
## Load required functions
library(faosws)
library(dplyr)
library(reshape2)
library(data.table)
library(faoswsUtil)
library(ggplot2)
library(countrycode)
library(scales)
library(VennDiagram)
library(knitr)

```

```{r include=FALSE, cache=FALSE}

foodCode = "5141"

DEBUG_MODE = Sys.getenv("R_DEBUG_MODE")
R_SWS_SHARE_PATH = Sys.getenv("R_SWS_SHARE_PATH")

if(!exists("DEBUG_MODE") || DEBUG_MODE == ""){
  token = "41558a20-c419-4821-8288-2dc7ccbc5ecf"
  GetTestEnvironment("https://hqlqasws1.hq.un.fao.org:8181/sws",token)

}

files = dir("~/Github/faoswsTourist/R", full.names = TRUE)
sapply(files, source)

## set the year range to pull data from the SWS
swsContext.computationParams$startYear <- as.numeric(swsContext.computationParams$startYear)
swsContext.computationParams$endYear <- as.numeric(swsContext.computationParams$endYear)
if(swsContext.computationParams$startYear > swsContext.computationParams$endYear)
    stop("First Year should be smallest than End Year")
## yearRange <- swsContext.datasets[[1]]@dimensions$timePointYears@keys
yearRange <- swsContext.computationParams$startYear:swsContext.computationParams$endYear
yearRange <- as.character(yearRange)

# Step 1: Pull the food consumption

## set the keys to get the calorie consumption, by individual FBS commodity for
## each country from the FAO working system
foodAreaCodes <- faosws::GetCodeList("agriculture", "aproduction", "geographicAreaM49")
foodElementCodes <- faosws::GetCodeList("suafbs", "fbs", "measuredElementSuaFbs")

## the Item codes contain a hierarchy.  We need to determine all the child
## nodes of the hierarchy and add them to get total consumption.
oldAreaCodes <- GetCodeList("agriculture", "aproduction", "geographicAreaM49")
itemCodes <- GetCodeList("agriculture", "aproduction", "measuredItemCPC")[, code]

## Pull the supply utilization account(SUA) food balance sheet (FBS) data from
## SWS pertaining to calorie consumption from each commodity in each country
countryCodeDim1 <- Dimension(name = "geographicAreaM49",
                             keys = oldAreaCodes[type == "country", code])
## A bit hackish: get population from total calories and total calories/person/day
foodCodeDim2 <- Dimension(name = "measuredElement", keys = c(foodCode))
itemCPCDim3 <- Dimension(name = "measuredItemCPC", keys = itemCodes)
timePointYearsDim4 <- Dimension(name = "timePointYears", keys = yearRange)
foodConsumptionKey <- DatasetKey(domain = "agriculture", dataset = "aproduction",
                                 dimensions = list(countryCodeDim1, foodCodeDim2, itemCPCDim3, timePointYearsDim4))

## download the calorie consumption data from the SWS
foodConsumptionData.1 <- GetData(foodConsumptionKey, flags = FALSE)

foodConsumptionData.1.1 <- dcast.data.table(foodConsumptionData.1,
                                            geographicAreaM49 + measuredItemCPC + timePointYears ~ measuredElement,
                                            value.var = "Value")

## set the column names to small simple ones representing destination cuntry, database
## element, year and total calories
setnames(foodConsumptionData.1.1, old = c("geographicAreaM49", "measuredItemCPC", "timePointYears", "5141"),
         new = c("country", "item", "year", "totalFood"))

# Pull calories data from each item using getNutrientConversionFactors function
foodConsumptionData.1.1[, valueCal := getNutrientConversionFactors(country, item)]

## Step 2: Pull the population datasets
countryCodePopDim1 <- Dimension(name = "geographicAreaM49",
                                keys = oldAreaCodes[type == "country", code])
elementPopDim2 <- Dimension(name = "measuredElementPopulation", keys = c("21"))
timePointYearsDim3 <- Dimension(name = "timePointYears", keys = yearRange)
popKey <- DatasetKey(domain = "population", dataset = "population",
                     dimensions = list(countryCodePopDim1, elementPopDim2, timePointYearsDim3))

## download the population data from the SWS
popData.2 <- GetData(popKey, flags = FALSE)

popData.2.1 <- dcast.data.table(popData.2,
                                geographicAreaM49 + timePointYears ~ measuredElementPopulation,
                                value.var = "Value")

## set the column names to small simple ones representing destination cuntry, 
##  year and total population
setnames(popData.2.1, old = c("geographicAreaM49", "timePointYears", "21"),
         new = c("country", "year", "pop"))

## Merge population data with food data
setkey(foodConsumptionData.1.1, "country", "year")
setkey(popData.2.1, "country", "year")

foodConsumptionPopData.3 <- merge(foodConsumptionData.1.1, popData.2.1, by = c("country", "year"), 
                                  all.x = TRUE )

## compute total calories per person per day in orig country
## Population is in 1000s
foodConsumptionPopData.3[, calPerPersonPerDay := (totalFood * valueCal * 10000) / 365 / (pop * 1000)]

## Compute the calorie consumption per country, per person and per day
calorieCountryDay.4 <- foodConsumptionPopData.3[, list(totalCalDay = sum(calPerPersonPerDay, na.rm=T)),
                                                by=list(country)]

## Let's to create the baseline consumption level (2500 calories per person per day).
calorieCountryDay.4[, baselineCalDay:= totalCalDay/2500]

## Step 3: Pull the tourist data
## set the keys to get the tourist data from the FAO working system
destinationAreaCodes <- faosws::GetCodeList("tourism", "tourist_flow",
                                            "destinationCountryM49")

originAreaCodes <- faosws::GetCodeList("tourism", "tourist_flow",
                                       "originCountryM49")

tourismElementCodes <- faosws::GetCodeList("tourism", "tourist_consumption",
                                           "tourismElement")

##Pull the bidirectional movement data from SWS pertaining to tourist visitors
##to all countries
destinationCountryDim1 <- Dimension(name = "destinationCountryM49",
                                    keys = destinationAreaCodes[, code])

originCountryDim2 <- Dimension(name = "originCountryM49",
                               keys = originAreaCodes[, code])

tourismElementDim3 <- Dimension(name = "tourismElement", keys = ("60"))
timePointYearsDim4 <- Dimension(name = "timePointYears", keys = yearRange)

touristKey <- DatasetKey(domain = "tourism", dataset = "tourist_flow",
                         dimensions = list(destinationCountryDim1, originCountryDim2, 
                                           tourismElementDim3, timePointYearsDim4))

## download the first tourist data from the SWS
touristData.5 <- GetData(touristKey, flags = FALSE)

cat("Tourist data loaded with ", nrow(touristData.5), " rows.")

## remove the tourismElement column which is of no value to me here
touristData.5 <- touristData.5[, which(!grepl("tourism", colnames(touristData.5))), 
                               with=FALSE]

## change column names to small simple ones representing destination, origin,
## year and overnight visitor number
setnames(touristData.5, old = c("destinationCountryM49", "originCountryM49", "timePointYears", "Value"), 
         new = c("dest", "orig", "year", "onVisNum"))

# Step 4: Pull the tourist consumption data
## set the keys to get the tourist data from the FAO working system
touristAreaCodes = faosws::GetCodeList("tourism", "tourist_consumption",
                                       "geographicAreaM49")

## Pull number of mean number of days stayed, and number of single-day visitors
## from SWS pertaining to visitors to all countries
consumptionCountryDim1 = Dimension(name = "geographicAreaM49", keys = touristAreaCodes [, code])
consumptionElementDim2 = Dimension(name = "tourismElement", keys = c("20", "30"))
timePointYearsDim3 = Dimension(name = "timePointYears", keys = yearRange)
consumptionKey = DatasetKey(domain = "tourism", dataset = "tourist_consumption",
                            dimensions = list(consumptionCountryDim1, consumptionElementDim2, timePointYearsDim3))

## download the bi-direction tourism data from the SWS
consumptionData.6 <- GetData(consumptionKey, flags = FALSE)

## set the column names to small simple ones representing destination, database
## element, year and value
setnames(consumptionData.6, old = c("geographicAreaM49", "tourismElement", "timePointYears", "Value"), 
         new = c("dest", "element", "year", "value"))

# Step 5: Calculate tourists leaving/coming to country A, B, ...

## cast the data table to get it in long format
consumptionData.6.1 <- as.data.table(dcast(consumptionData.6, dest + year ~ element))

## change the column names to something readable, "onVisDays" stands for the
## mean number of days that overnight visitors stayed in the destination country.
## "totDayVisNum" is the number of people who visited the country but for a
## single day, e.g. from a cruise ship
setnames(consumptionData.6.1, old = c("20", "30"), 
         new = c("onVisDays", "totDayVisNum"))

## replace missing day visitor numbers (NA) with zero, because it won't effect
## end calculations, but NA's cause equations to fail
consumptionData.6.1$totDayVisNum[is.na(consumptionData.6.1$totDayVisNum)] <- 0

## merge the two data sets, one containing overnight visitor numbers and number
## of days they visited, the other data set the number of tourists travelling to
## and from each country
touristOverNightData.7 <- merge(touristData.5, consumptionData.6.1, 
                                by=c("dest", "year"), all.x = TRUE)

## rearrange the column order to make it easier to view
touristOverNightData.7 <- setcolorder(touristOverNightData.7, neworder = c("year", "orig", "dest", "onVisNum",
                                                                           "onVisDays", "totDayVisNum"))

## a small number of countries are missing values for overnight visitor days,
## "onVisDays" and this affects the bi-directional calculations for them, but
## also all of the other countries as well, so this imputes the missing number
## of days, by taking the mean of all day numbers present, grouped by year.
touristOverNightData.7[, onVisDays := ifelse(is.na(onVisDays), mean(onVisDays, na.rm=TRUE),
                                             onVisDays), by = year]

## calculate the total number tourist visitor days, the product of overnight
## visitor number and days per visit
touristOverNightData.7[, onVisTotDays := onVisNum * onVisDays]

## calculate a new total overnight visitor number per country of destination, to
## be used later to proportion the day visitor number, because we do not have
## data for country of origin, and allocate them to a country of origin,
## assuming they arrive in the same relative proportions as the overnight
## visitors
touristOverNightData.7[, totOnVisNum := sum(onVisNum), 
                       by=list(year,dest)]

## create a new total visitor days by summing the overnight visitor days, and
## the day visitor days
touristOverNightData.7[, totVisDays := onVisTotDays + totDayVisNum]

## We need to merge touristOverNightData.7 with calorieCountryDay.4 to calculate
## the consumption in each country. In our approach, the person comes from country A
## to country B eats the same food types as people in country B but eats the same
## calorie amounts as in their home country. In case we don't have totalCalDay for
## the country A, we will assume the same calories amount in country B.

# Merge by orig country
touristOverNightData.7.1 <- merge(touristOverNightData.7, calorieCountryDay.4, 
                                  by.x="orig", by.y="country", all.x=T)
setnames(touristOverNightData.7.1, old="baselineCalDay", new="baselineCalDayOrigCountry")
touristOverNightData.7.1[, totalCalDay := NULL]

# Merge by dest country
touristOverNightData.7.2 <- merge(touristOverNightData.7.1, calorieCountryDay.4, 
                                  by.x="dest", by.y="country", all.x=T)
setnames(touristOverNightData.7.2, old="baselineCalDay", new="baselineCalDayDestCountry")
touristOverNightData.7.2[, totalCalDay := NULL]

touristOverNightData.7.2[, baselineCalDayOrigCountry := ifelse(is.na(baselineCalDayOrigCountry), baselineCalDayDestCountry, 
                                                               baselineCalDayOrigCountry)]
# Now, we'll use only the baselineCalDayOrigCountry.
touristOverNightData.7.2[, baselineCalDayDestCountry := NULL]

## calculate total visitor days per year who leaves your country using the baseline
daysOut.8 <- touristOverNightData.7.2[, list(daysOut = sum(totVisDays * baselineCalDayOrigCountry, na.rm=T)),
                                      by = c('orig', 'year')]

## calculate total visitor days per year who comes to the country
daysIn.9 <- touristOverNightData.7.2[, list(daysIn = sum(totVisDays * baselineCalDayOrigCountry, na.rm=T)),
                                     by = c('dest', 'year')]

## change column name from "orig" to "country"
setnames(daysOut.8, 'orig', 'country')

## change column name from "dest" to "country"
setnames(daysIn.9, 'dest', 'country')

##-------------
## tourist data
##-------------

## merge daysOut and daysIn to allow calculation of days net per country and year
tourismDays.10 <- merge(daysOut.8, daysIn.9, by=c("country", "year"), all.x = TRUE)
tourismDays.10[, daysNet := daysIn - daysOut]

## Merge tourismDays.10 with the food consumption data
setkey(tourismDays.10, "country", "year")
setkey(foodConsumptionPopData.3, "country", "year")

foodTouristConsumption.11 <- merge(foodConsumptionPopData.3, tourismDays.10, by = c("country", "year"), 
                                   all.x = T)

foodTouristConsumption.11[, calOutCountry := daysOut * calPerPersonPerDay]
foodTouristConsumption.11[, calInCountry := daysIn * calPerPersonPerDay]
foodTouristConsumption.11[, calNetCountry := daysNet * calPerPersonPerDay]

## making some manipulations

# calculating the calorie amount by the population
foodTouristConsumption.11[, caloriesByPop := calPerPersonPerDay * pop * 1000 * 365]


## Get rid of some of the columns that we don't need anymore:
foodTouristConsumption.11[, c("totalFood", "valueCal", "calPerPersonPerDay", "daysOut", 
                              "daysIn", "daysNet") := NULL]

cpcCode <- GetCodeList("agriculture", "aproduction", "measuredItemCPC")[, code, description]
setnames(cpcCode, old = c("description", "code"), new = c("Item", "item"))

m49Code <- GetCodeList("agriculture", "aproduction", "geographicAreaM49")[, code, description]
setnames(m49Code, old = c("description", "code"), new = c("Country", "country"))

## Merge
touristCaloriesData <- merge(foodTouristConsumption.11, m49Code, by = c("country"), all.x = T)
touristCaloriesData <- merge(touristCaloriesData, cpcCode, by = c("item"), all.x = T)

setnames(touristCaloriesData, old=c("Country", "Item"), new=c("countryName", "itemName"))

setcolorder(touristCaloriesData, neworder=c("year", "pop", "country", "countryName", "item", "itemName", 
                                            "caloriesByPop", "calOutCountry", "calInCountry", "calNetCountry"))

## % consumption per country
tabCountry <- touristCaloriesData[, list(percentNetCal = sum(calNetCountry, na.rm=T)/sum(caloriesByPop, na.rm=T),
                                         percentInCal = sum(calInCountry, na.rm=T)/sum(caloriesByPop, na.rm=T),
                                         percentOutCal = sum(calOutCountry, na.rm=T)/sum(caloriesByPop, na.rm=T),
                                         pop = max(pop)),
                                 by = list(year, country, countryName)]
# we have 4 Chinas ("China, Macao", "China,H.Kong", etc...). We'll exclude here because we don'w have data for China just.
tabCountry <- tabCountry[!grepl("China", countryName)]

````

```{r include=FALSE, cache=FALSE}
## world map is working now
## Load fao_world object
load(url("https://github.com/UNFAOstatistics/gisfao/raw/master/data/fao_world.RData"))
# Install development version of ggplot2
#devtools::install_github("hadley/ggplot2")
coords <- ggplot2:::fortify(fao_world)
countryMap <- as.character(fao_world$ADM0_NAME)
countryMap <- data.frame(id = 0:(length(countryMap)-1),
                         country = countryMap)
coords <- merge(coords, countryMap, by = "id", all = TRUE)

# Let's to exclude the countries that don't have tourist data
tabCountry <- tabCountry[!(percentNetCal == 0) & 
                           !(percentNetCal == "NaN" & percentInCal == "NaN" & percentOutCal == "NaN")]
## use countryCode package
tabCountry <- data.frame(tabCountry)
tabCountry$shortName <- countrycode(tabCountry$countryName, "country.name", "iso3c")

coords$shortName <- countrycode(coords$country, "country.name", "iso3c")
# unique(subset(coords, is.na(shortName) == T)$country)

coords <- merge(coords, tabCountry, by = "shortName", all = TRUE)
coords <- coords[order(coords$shortName, coords$piece, coords$order), ]

## Create a categorical variable
coords <- data.table(coords)
coords[, percentCat := ifelse(is.na(percentNetCal) == T, "Missing", 
                               ifelse(percentNetCal > 0, "Receiver",
                                     ifelse(percentNetCal < 0, "Emitter", "Neutro")))]

coords$percentCat <- factor(coords$percentCat, 
                             levels = c("Missing", "Emitter", "Neutro", "Receiver"))

coords <- coords[!is.na(country.x)]

````

## Segmentation of the world according to a tourist consumption


For our first visualization, we divided the countries in three clusters.


**Receiver**: countries with net food consume by tourists more than 0.

**Emitter**: countries with net food consume by tourists less than 0.

**Missing**: countries with no data for tourist consumption.

There are information for 128 countries (68.5%) and the others countries have missing data.

According to a cluster, we have:

````{r, echo=FALSE}

tabCountryCluster <- coords[, list(percentCat = max(percentCat)), 
                            by=list(country.x)]

tab = tabCountryCluster[, .N, percentCat]
tab[, percent:=100*round(N/sum(N), 2)]

kable(tab, format = "markdown", padding = 0, 
      col.names=c("Cluster", "Number of countries", "%"))
````


````{r, echo=FALSE}
options(warn=-1)
ggplot(coords, aes(x=long, y=lat, group=group, fill=percentCat)) + 
  geom_polygon(color="white") + #theme(legend.title=element_blank()) +
  scale_fill_manual(values=c("#C0C0C0", "#D00000", "#2E8B57", "#667bc6", "#2E8B57")) +
  #geom_point() + 
  #geom_text(label=country.x) +
  theme(#line = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        #text = element_blank(),
        title = element_blank())
````

## Summaries


Above there are some statistics about the **Net Tourist Consumption** estimated by **Tourist Module**.

Note that when the estimates for tourist consumption is **negative** it means that more people **left this country**. If is **positive**, it means that more people **went** to this country.

````{r, echo=FALSE}
tabCountry <- data.table(tabCountry)
kable(tabCountry[, list(min=100*round(min(percentNetCal), 3), mean=100*round(mean(percentNetCal), 3), max=100*round(max(percentNetCal), 3))], format = "markdown", padding = 3, col.names=c("Min", "Mean", "Max"))
````

This result it means that the country more impacted with the tourist consumption had **`r paste0(100*round(max(tabCountry$percentNetCal), 3), '%')`** of your production consumed by tourists. 
So we can calculate which countries were more impacted with the tourist consumption and which ones had less tourist consumption in 2012.

The histogram above is about the net food consumption % of tourists.

````{r, echo=FALSE}
hist(100*tabCountry$percentNetCal, breaks = 100, xlab = "Net Food Consumption % of Tourists", main="")
````

## Countries more impacted by Tourist Consumption

Into some small islands states which are popular holiday destinations, such as the Bahamas or Seychelles, the Tourist Consumption can constituite a significant part in the uses of food products.

````{r, echo=FALSE}

tabCountry <- tabCountry[order(-percentNetCal)]
top5 <- head(tabCountry[, c("countryName", "percentNetCal"), with=F], 5)
top5[, percentNetCal:= 100*round(percentNetCal, 3)]
kable(top5, format = "markdown", padding = 3, col.names=c("Country", "% Tourist Consumption"))
````

## Countries less impacted by Tourist Consumption

These countries are the less impacted by tourist consumption. It means that more people left these countries than went to these countries.

````{r, echo=FALSE}

tabCountry <- tabCountry[order(percentNetCal)]
top5Less <- head(tabCountry[, c("countryName", "percentNetCal"), with=F], 5)
top5Less[, percentNetCal:= 100*round(percentNetCal, 3)]
kable(top5Less, format = "markdown", padding = 3, col.names=c("Country", "% Tourist Consumption"))
````

## Tourist consumption for the 5 biggest countries by population
````{r, echo=FALSE}

tabCountry <- tabCountry[order(-pop)]
top5Big <- head(tabCountry[, c("countryName", "percentNetCal"), with=F], 5)
top5Big[, percentNetCal:= 100*round(percentNetCal, 3)]
kable(top5Big, format = "markdown", padding = 3, col.names=c("Country", "% Tourist Consumption"))
````

## Tourist consumption for the 5 smallest countries by population

````{r, echo=FALSE}

tabCountry <- tabCountry[order(pop)]
top5Small <- head(tabCountry[, c("countryName", "percentNetCal"), with=F], 5)
top5Small[, percentNetCal:= 100*round(percentNetCal, 3)]
kable(top5Small, format = "markdown", padding = 3, col.names=c("Country", "% Tourist Consumption"))
````
